### 2018-08-07 paper/evaluation.tex
bandwidth
new figure

>>>>

\begin{figure}[t]
  \centering
  %\def\svgwidth{0.8\columnwidth}
  \includegraphics[width=\columnwidth]{figures/bw_and_pending_files.pdf}

  \caption{\label{fig:bw_and_pending_files}In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
\end{figure}

\begin{figure}[t]
  \centering
  %\def\svgwidth{0.8\columnwidth}
  \includegraphics[width=\columnwidth]{figures/bw_and_pending_files_log.pdf}

  \caption{\label{fig:bw_and_pending_files_log}In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
\end{figure}
